\chapter{Related Work}
wie haben die anderen diese variablen untersucht
wie wurden die variablen untersucht $\rightarrow$ studiensetting
%----------------------------------------------------
\section{MR learning systems}
\begin{itemize}
	\item one body:
	\item vr dance trainer:
	\item you move:
	\item training archived physical skills:
	\item
	\item teaching traditional dance using e-learning tools, bakogianni
\end{itemize}

%----------------------------------------------------
\section{Ego/exo perspective work - if exists}
\begin{itemize}
	\item training archived physical skill: seamless change from first to third person
\end{itemize}
%----------------------------------------------------
\section{variables}
\begin{itemize}
	\item independent/dependent variables
	\item measures
	\item task: reuse or adapt existing task
\end{itemize}
%----------------------------------------------------
\subsection{Task}
\begin{itemize}
	\item Onebody: 16 artificial postures not from but like: tai chi, matial arts
	\item VR Dance Trainer: dance movements, 15 min for each move
	\item you move: various movements to perform. using a whip, baseball, boxing, ballet, dance moves
	\item training archived physical skills IVE: physical skills in sport activities, especially baseball pitching
\end{itemize}
%----------------------------------------------------
\subsection{Measures}
\begin{itemize}
	\item scientific work, how to measure movements: hachimura et al, yoshimura et al, qian et al, kwon et al, all use joint angles,  (mentioned in: vr dance trainer)
	\item onebody: skeletal tracking, how much percent do the postures match? 3d positions of limbs measured: wrist, elbow, shoulder, hip knee ankle. so angle between bones is the main measure for accuracy. additionally a subjective instructor score was recorded. And, completion time, topped by 2 min.
	\item VR Dance trainer: there are 3 common features for measuring hte difference between movements: joint position, velocity, angle. they tested which feature descibes movements best: joint position. base line vs post training movements are compared.
	\item you move: in each keyframe, score based on the joint with the maximum error, measured in euclidean distance. but only "important joints" are measured. timing errors: 0.5s error on each side of the frame for matching posture. is timing important, the window is reduced to 0.25s. max eucl. distance is linear mapped to a score. 0 error is 10 (max), 10cm is 7.5 what is the score to pass. if precision is important, 10cm needed for pass.
\end{itemize}
%----------------------------------------------------
\section{Body parts included}
\begin{itemize}
	\item onebody
	\item vr dance trainer
	\item you move: full body
	\item training archived physical skill: full body
\end{itemize}
%----------------------------------------------------
\subsection{training method}
\begin{itemize}
	\item one body:
	\item vr dance trainer:
	\item you move: 
	\item training archived physical skill: key frame method
\end{itemize}
%----------------------------------------------------
\subsection{tracking technology}
\begin{itemize}
	\item 
	\item 
	\item 
	\item training archived physical skills: kinect
\end{itemize}
%----------------------------------------------------
\subsection{display technology}
\begin{itemize}
	\item
	\item 
	\item 
	\item training archived physical skills: low res HMD (oculus rift dk1/dk2)
\end{itemize}
%----------------------------------------------------
\subsection{Independent and Dependent Variables}
\subsubsection{Dependent Variables}
\begin{itemize}
	\item VR
	\item bilateral movements
	\item Movement types: synchronous  / asynchronous 
\end{itemize}
\subsubsection{Independent Variables}
\begin{itemize}
	\item Body parts: upper body (UB), lower body (LB), full body (FB)
	\item Perspective: Ego, Exo, Ego/Exo combined
	\item Movement types: synchronous  / asynchronous 
\end{itemize}
%----------------------------------------------------
\section{How do we learn movements}

%----------------------------------------------------
\section{how to quantify movements}
Judging motions and their matching to a given motion is not a trivial task. One approach follows Rudolph von Laban who was a professional dancer. Von Laban developed a broadly used dance notation. His work lead to the \textit{Laban Movement Analysis} with which a human movements could be quantized.\footnote{Brockhaus, Rudolf Laban. http://www.brockhaus.de/ecs/enzy/article/laban-rudolf (accessed 2018-10-25)} There are four main components to systematically describe movements in the \textit{Laban Movement Analysis}: body, effort, shape and space. Each component can describe movements independently or combined. Hachimura et al. \todo used the methodology  of \textit{Laban Movement Analysis} and adopted it to for digital movements.\\
Yoshimura et al. \todo followed a similar approach from another dance movement description theory called \textit{furi}. \textit{Furi} is also described by four so called \textit{indices}: \textit{kamae}, \textit{jyu-shin}, \textit{koshi}, \textit{uchiwa}. Yoshimura at all could map these indices to concrete markers on the body of a performer. They showed that there was a significant difference between movements by an expert and a beginner. Qian et al. \todo developed a gesture recognition system for performing arts. To match the motions ten body parts were defined: head, torso, upper arms, forearms, upper legs and lower legs. For each body part the Mahalanobis distance is calculated to an ideal point. The Mahalonobis distance describes the distance between a point \textit{p} and a distribution \textit{D}. Kwon et al. \todo 
\begin{itemize}
	\item K. Hachimura, K. Takashina, and M. Yoshimura, “Analysis and
	Evaluation of Dancing Movement Based on LMA,” Proc. IEEE Int’l
	Workshop Robots and Human Interactive Comm., pp. 294-299, 2005.
	\item M. Yoshimura, N. Mine, T. Kai, and L. Yoshimura, “Quantification	of Characteristic Features of Japanese Dance for Individuality Recognition,” Proc. IEEE Int’l Workshop Robot and Human Interactive Comm., pp. 193-199, Sept. 2001.
	\item G. Qian, F. Guo, T. Ingalls, L. Olson, J. James, and T. Rikakis, “A	Gesture-Driven Multimodal Interactive Dance System,” Proc. IEEE	Int’l Conf. Multimedia and Expo (ICME ’04), pp. 1579-1582, June	2004.
	\item D.Y. Kwon and M. Cross, “Combining Body Sensors and Visual
	Sensors for Motion Training,” Proc. ACM SIGCHI, pp. 94-101,	2005.
	\item vr dance trainer
\end{itemize}
%----------------------------------------------------
\section{Conclusion}
\begin{itemize}
	\item task is xyz because of abc
	\item measures are xyz because of abc
	\item variables are...
\end{itemize}
